---
title: "results_testing"
author: "Holly Hake"
date: "8/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(tidyverse)
library(dplyr)
library(broom)
library(reshape2)
library(glmnet)
library(readr)

## Graphics
library(ggplot2)
library(ggthemes)
library(ggrepel)
library(ppcor)
library(ggExtra)
library(ggsci)
library(viridis)
library(scales)
library(patchwork)# Multi-plot alignment
library(ggcorrplot)
library(gapminder) # dataset used to make the box plot connected by lines
library(RColorBrewer) 
library(plotly) # Added to make interactive graphs 
library(lubridate) # Added to make interactive graphs; use different date funcs
library(stringr) # Added to make interactive graphs; use different txt funcs
library(extrafont) # Added to make interactive graphs; change font on graphs
library(htmlwidgets) # Added to make interactive graphs; make exports interactive
library(cowplot)

## Tables
library(kableExtra)
library(xtable)

# Date functions
library(anytime)
library(lubridate)

# SlimStampen

#install.packages("devtools") # Install SlimStampen packages. Instructions on https://github.com/VanRijnLab/SlimStampeRData
library(devtools)
#devtools::install_github("VanRijnLab/SlimStampeRData",
                      #   build_vignettes = TRUE,
                       #  dependencies = TRUE,
                        # force = TRUE) 
# The console will show a prompt asking whether all packages should be updated. Select option 1 (by typing 1 and then pressing enter), this will update all packages.
vignette("SlimStampeRVignette")
library(SlimStampeRData)

```

```{r, echo=FALSE, results= 'hide'}

# Load data
load("C:/Users/17203/Documents/GitHub/Blaarkop/data/SlimStampen_2022-08-05.RData")

# Filter for just ADRC subjects & group by clinical status
groups <- read_csv("C:/Users/17203/Documents/GitHub/Blaarkop/groups.csv", show_col_types = FALSE)
data %>% 
  filter(userId %in% groups$userId) -> data


```

```{r, echo=FALSE, results= 'hide'}

# Calculate fact rep, activation, and alpha 
MAX_ALPHA=0.8
data <- data %>%
  calculate_repetition() %>%
  calculate_alpha_and_activation(maxAlpha=MAX_ALPHA)

```

```{r}
# Filter the sessions
sessionData <- data %>% 
  group_by(userId, sessionId, lessonId, lessonTitle) %>% 
  summarize(duration = (max(presentationStartTime) - min(presentationStartTime))/60000,
            start = min(presentationStartTime),
            legit = if_else(duration > 6, T, F)) 

sessionData <- sessionData %>% 
  group_by(userId, lessonId, lessonTitle, factAnswer, reactionTime) %>% 
  arrange(start, by_group=T) %>%
  mutate(sessionRank = seq(1, length(start)))

sessionDataFiltered <- sessionData %>%
  filter(legit == T) %>%
  group_by(userId, lessonId, lessonTitle, factAnswer, reactionTime) %>%
  mutate(minRank = min(sessionRank))

sessionData <- sessionData %>%
  inner_join(sessionDataFiltered) %>%
  mutate(usable = if_else(minRank == sessionRank, T, F))

```

```{r}

















```{r, echo=FALSE, results= 'hide'}
# Filter by task  
Pasta=filter(data,lessonTitle=='Pasta')
Swahili1=filter(data,lessonTitle=='Swahili 1')
Flowers=filter(data,lessonTitle=='Flowers')  
Capitals=filter(data,lessonTitle=='European Capitals 1') 
Birds=filter(data,lessonTitle=='Birds') 
News=filter(data,lessonTitle=='Newspapers') 
Flags=filter(data,lessonTitle=='Asian Flags') 
Folktales=filter(data,lessonTitle=='Folktales')






```


```{r, echo=FALSE, results= 'hide'}

# Function
## Average Rate of Forgetting for Every Fact 

average_ROF_facts <- function(data, factNames = "factId", xlim = NULL, ylim = NULL) {
  if(missing(data)){
    stop("No data is provided")
  }
  if(!("repetition" %in% colnames(data))){
    stop("No repetition column is provided in the data, run calculate_repetition() to add a repetition column to the data")
  }
  if(!("alpha" %in% colnames(data))){
    stop("No alpha column is provided in the data, run calculate_alpha_and_activation() to add an alpha column to the data")
  }

  if(!(is.null(xlim) | length(xlim) == 2)){
    stop("xlim must be a vector of 2")
  }
  if(!(is.null(ylim) | length(ylim) == 2)){
    stop("ylim must be a vector of 2")
  }
  
  # Prints a message when the column contains missing values
missing_values_message <- function(data, columns) {
  indx <- apply(data, 2, function(x) any(is.na(x)))
  for(col in columns){
    if(col %in% colnames(data)[indx]){
      cat("! There are missing values in the column ", col, " ! \n")
    }
  }
}

# Returns a non-empty vector when a column is missing
  
  missing_columns_check <- function(data, columns) {
  missingcols <- character(0)
  for(col in columns){
    if(!(col %in% colnames(data))){
      missingcols[[1]] <- col
    }
  }
  return(missingcols)
}
  
  missingcol <- missing_columns_check(data, c("sessionId", "alpha", "repetition", "factId", "lessonId", "userId", "presentationStartTime", factNames))
  if(length(missingcol) > 0){
    stop("No ", missingcol[[1]] ," column is provided in the data")
  }

  if(-1 %in% data$factId){
    data <- resetremoval(data)
    cat("- There are resets present in the data. Reset data is excluded in this function. - \n")
  }

  missing_values_message(data, c("sessionId", "alpha", "repetition", "factId", factNames))

  #Only the first session of a user within a lesson is kept in the data
firstsession <- function(df) {
  dfgroup <- dplyr::group_by(df, lessonId, userId)
  dfsort <- dplyr::arrange(dfgroup, presentationStartTime, .by_group = TRUE)
  dfclean <- dplyr::filter(dfsort, sessionId == unique(sessionId)[1])
  dffree <- dplyr::ungroup(dfclean)
  return(dffree)
}
  
  data <- firstsession(data)

  cat("This may take a moment... \n")
  plotTitle <- paste("Rate of Forgetting for Each Fact")
  plot <- NULL

  facts <- sort(unique(data$factId))
  factcolor <- viridis::turbo(length(facts))
  names(factcolor)  <- facts

  # Group by sessionId and repetition, then mean alpha as new column
  dat1 <- dplyr::group_by(.data = data, factId, repetition)
  dat2 <- dplyr::summarise(.data = dat1, mean_alpha = mean(alpha, na.rm=TRUE), factLabels = unique(.data[[factNames]])[[1]])
  dat2$factLabels = substr(dat2$factLabels, 1, 10)
  dat3 <- dplyr::group_by(.data = dat2, factId)
  dat4 <- dplyr::filter(.data = dat3, repetition == max(repetition))
  dat5 <- dat4[order(dat4$mean_alpha, decreasing = TRUE),]

  y = ylim
  x = xlim

  # Make plot HH
  plot <- ggplot2::ggplot(data = dat2, ggplot2::aes(x = factor(repetition), y = mean_alpha, group = factId)) +
    ggplot2::geom_line(alpha = 1, ggplot2::aes(colour = factor(factId))) +
    ggplot2::geom_point(alpha = 0.5, size = 1, ggplot2::aes(colour = factor(factId), fill = factor(factId))) +
    ggplot2::geom_point(data = dat5, alpha = 0.5, size = 3, position = ggplot2::position_jitter(w = 0.08, h = 0), ggplot2::aes(colour = factor(factId), fill = factor(factId))) +
    ggplot2::scale_color_manual(name="Facts", labels = dat5$factLabels,values = factcolor, breaks=dat5$factId) +
    ggplot2::guides(fill = "none") +
    ggplot2::coord_cartesian(xlim = x, ylim = y) +
    ggplot2::labs(x = "Fact Repetitions", y = "Alpha") +
    theme_pander() +
    ggplot2::theme(legend.position="right") +
    ggplot2::guides(colour=ggplot2::guide_legend(nrow=18, byrow=FALSE)) +
    ggplot2::ggtitle(plotTitle)
  
  plot
  
}
```


```{r, echo=FALSE, results= 'hide'}

# Function
## Average Rate of Forgetting for Every Participant in Each Lesson (Interactive)
### Interactive

average_ROF_participants_interactive <- function(data, xlim = NULL, ylim = NULL, userId = "userId") {
  if(missing(data)){
    stop("No data is provided")
  }
  if(!("repetition" %in% colnames(data))){
    stop("No repetition column is provided in the data, run calculate_repetition() to add a repetition column to the data")
  }
  if(!("alpha" %in% colnames(data))){
    stop("No alpha column is provided in the data, run calculate_alpha_and_activation() to add an alpha column to the data")
  }
  
    # Prints a message when the column contains missing values
missing_values_message <- function(data, columns) {
  indx <- apply(data, 2, function(x) any(is.na(x)))
  for(col in columns){
    if(col %in% colnames(data)[indx]){
      cat("! There are missing values in the column ", col, " ! \n")
    }
  }
}

# Returns a non-empty vector when a column is missing
  
  missing_columns_check <- function(data, columns) {
  missingcols <- character(0)
  for(col in columns){
    if(!(col %in% colnames(data))){
      missingcols[[1]] <- col
    }
  }
  return(missingcols)
}
  
  missingcol <- missing_columns_check(data, c("sessionId", "alpha", "repetition", "lessonId", "userId", "presentationStartTime", "factId"))
  if(length(missingcol) > 0){
    stop("No ", missingcol[[1]] ," column is provided in the data")
  }

  if(!(is.null(xlim) | length(xlim) == 2)){
    stop("xlim must be a vector of 2")
  }
  if(!(is.null(ylim) | length(ylim) == 2)){
    stop("ylim must be a vector of 2")
  }

  if(-1 %in% data$factId){
    data <- resetremoval(data)
    cat("- There are resets present in the data. Reset data is excluded in this function. - \n")
  }

  missing_values_message(data, c("sessionId", "alpha", "repetition"))
  
    #Only the first session of a user within a lesson is kept in the data
firstsession <- function(df) {
  dfgroup <- dplyr::group_by(df, lessonId, userId)
  dfsort <- dplyr::arrange(dfgroup, presentationStartTime, .by_group = TRUE)
  dfclean <- dplyr::filter(dfsort, sessionId == unique(sessionId)[1])
  dffree <- dplyr::ungroup(dfclean)
  return(dffree)
}

  data <- firstsession(data)

  participants <- sort(unique(data$userId))
  partcolor <- viridis::turbo(length(participants))
  names(partcolor)  <- participants

  cat("This may take a moment... \n")
  plotTitle <- paste("RoF for Each Participant")
  plot <- NULL

  # Group by sessionId and repetition, then mean alpha as new column
  dat1 <- dplyr::group_by(.data = data, userId, repetition)
  dat2 <- dplyr::summarise(.data = dat1, mean_alpha = mean(alpha, na.rm=TRUE),Participant = unique(.data[[userId]])[[1]])
  dat2$Participant = substr(dat2$Participant, 1, 10)
  dat3 <- dplyr::group_by(.data = dat2, userId)
  dat4 <- dplyr::filter(.data = dat3, repetition == max(repetition))
  dat5 <- dat4[order(dat4$mean_alpha, decreasing = TRUE),]

  y = ylim
  x = xlim

  # Make plot
  graph.clinical=ggplot2::ggplot(data = dat2, ggplot2::aes(x = factor(repetition), y = mean_alpha, group = userId, text=paste0(userId))) +
    ggplot2::geom_line(alpha = 1, ggplot2::aes(colour = factor(userId))) +
    ggplot2::geom_point(alpha = 0.5, size = 1, ggplot2::aes(colour = factor(userId), fill = factor(userId))) +
    ggplot2::geom_point(data = dat5, alpha = 0.5, size = 3, position = ggplot2::position_jitter(w = 0.08, h = 0), ggplot2::aes(colour = factor(userId), fill = factor(userId))) +
    ggplot2::scale_color_manual(name="Participants", labels = dat5$Participant,values = partcolor, breaks=dat5$userId) +
    ggplot2::guides(fill = "none") +
    ggplot2::coord_cartesian(xlim = x, ylim = y) +
    ggplot2::labs(x = "Fact Repetitions", y = "Alpha") +
    theme_pander() +
    ggplot2::theme(legend.position="none") +
    ggplot2::guides(colour=ggplot2::guide_legend(nrow=18, byrow=FALSE)) +
    ggplot2::ggtitle(plotTitle)
    
  ggplotly(graph.clinical, tooltip=c("y", "text")) %>% 
  layout(legend = list(orientation = "h")) %>% 
  config(displayModeBar=FALSE)
    
}    
```


```{r}

# Function
## Average Rate of Forgetting for Every Participant in Each Lesson

average_ROF_participants <- function(data, xlim = NULL, ylim = NULL, userId = "userId") {
  if(missing(data)){
    stop("No data is provided")
  }
  if(!("repetition" %in% colnames(data))){
    stop("No repetition column is provided in the data, run calculate_repetition() to add a repetition column to the data")
  }
  if(!("alpha" %in% colnames(data))){
    stop("No alpha column is provided in the data, run calculate_alpha_and_activation() to add an alpha column to the data")
  }
  
    # Prints a message when the column contains missing values
missing_values_message <- function(data, columns) {
  indx <- apply(data, 2, function(x) any(is.na(x)))
  for(col in columns){
    if(col %in% colnames(data)[indx]){
      cat("! There are missing values in the column ", col, " ! \n")
    }
  }
}

# Returns a non-empty vector when a column is missing
  
  missing_columns_check <- function(data, columns) {
  missingcols <- character(0)
  for(col in columns){
    if(!(col %in% colnames(data))){
      missingcols[[1]] <- col
    }
  }
  return(missingcols)
}
  
  missingcol <- missing_columns_check(data, c("sessionId", "alpha", "repetition", "lessonId", "userId", "presentationStartTime", "factId"))
  if(length(missingcol) > 0){
    stop("No ", missingcol[[1]] ," column is provided in the data")
  }

  if(!(is.null(xlim) | length(xlim) == 2)){
    stop("xlim must be a vector of 2")
  }
  if(!(is.null(ylim) | length(ylim) == 2)){
    stop("ylim must be a vector of 2")
  }

  if(-1 %in% data$factId){
    data <- resetremoval(data)
    cat("- There are resets present in the data. Reset data is excluded in this function. - \n")
  }

  missing_values_message(data, c("sessionId", "alpha", "repetition"))
  
    #Only the first session of a user within a lesson is kept in the data
firstsession <- function(df) {
  dfgroup <- dplyr::group_by(df, lessonId, userId)
  dfsort <- dplyr::arrange(dfgroup, presentationStartTime, .by_group = TRUE)
  dfclean <- dplyr::filter(dfsort, sessionId == unique(sessionId)[1])
  dffree <- dplyr::ungroup(dfclean)
  return(dffree)
}

  data <- firstsession(data)

  participants <- sort(unique(data$userId))
  partcolor <- viridis::turbo(length(participants))
  names(partcolor)  <- participants

  cat("This may take a moment... \n")
  plotTitle <- paste("RoF for Each Participant")
  plot <- NULL

  # Group by sessionId and repetition, then mean alpha as new column
  dat1 <- dplyr::group_by(.data = data, userId, repetition)
  dat2 <- dplyr::summarise(.data = dat1, mean_alpha = mean(alpha, na.rm=TRUE),Participant = unique(.data[[userId]])[[1]])
  dat2$Participant = substr(dat2$Participant, 1, 10)
  dat3 <- dplyr::group_by(.data = dat2, userId)
  dat4 <- dplyr::filter(.data = dat3, repetition == max(repetition))
  dat5 <- dat4[order(dat4$mean_alpha, decreasing = TRUE),]

  y = ylim
  x = xlim

  # Make plot
  plot <- ggplot2::ggplot(data = dat2, ggplot2::aes(x = factor(repetition), y = mean_alpha, group = userId)) +
    ggplot2::geom_line(alpha = 1, ggplot2::aes(colour = factor(userId))) +
    ggplot2::geom_point(alpha = 0.5, size = 1, ggplot2::aes(colour = factor(userId), fill = factor(userId))) +
    ggplot2::geom_point(data = dat5, alpha = 0.5, size = 3, position = ggplot2::position_jitter(w = 0.08, h = 0), ggplot2::aes(colour = factor(userId), fill = factor(userId))) +
    ggplot2::scale_color_manual(name="Participants", labels = dat5$Participant,values = partcolor, breaks=dat5$userId) +
    ggplot2::guides(fill = "none") +
    ggplot2::coord_cartesian(xlim = x, ylim = y) +
    ggplot2::labs(x = "Fact Repetitions", y = "Alpha") +
    theme_pander() +
    ggplot2::theme(legend.position="right") +
    ggplot2::guides(colour=ggplot2::guide_legend(nrow=18, byrow=FALSE)) +
    ggplot2::ggtitle(plotTitle)
    
  plot

    
}   

```

## Average Rate of Forgetting for Every Fact 

```{r}
average_ROF_facts(Pasta, factNames = "factAnswer")
average_ROF_facts(Swahili1, factNames = "factAnswer")
average_ROF_facts(Flowers, factNames = "factAnswer")
average_ROF_facts(Capitals, factNames = "factAnswer")
average_ROF_facts(Birds, factNames = "factAnswer")
average_ROF_facts(News, factNames = "factAnswer")
average_ROF_facts(Flags, factNames = "factAnswer")

```

## Average Rate of Forgetting for Every Participant in Each Lesson (Interactive)

```{r}
average_ROF_participants_interactive(Pasta, userId = "userId")
average_ROF_participants_interactive(Swahili1, userId = "userId")
average_ROF_participants_interactive(Flowers, userId = "userId")
average_ROF_participants_interactive(Capitals, userId = "userId")
average_ROF_participants_interactive(Birds, userId = "userId")
average_ROF_participants_interactive(News, userId = "userId")
average_ROF_participants_interactive(Flags, userId = "userId")

```

## Average Rate of Forgetting for Every Participant in Each Lesson

```{r}
average_ROF_participants(Pasta, userId = "userId")
average_ROF_participants(Swahili1, userId = "userId")
average_ROF_participants(Flowers, userId = "userId")
average_ROF_participants(Capitals, userId = "userId")
average_ROF_participants(Birds, userId = "userId")
average_ROF_participants(News, userId = "userId")
average_ROF_participants(Flags, userId = "userId")

```

```{r}

# generate more illustrative dataset: you have this already
set.seed(1)
x <- 1:1000
y <- as.POSIXct("06/01/2013",format="%m/%d/%Y")+sample(0:(210*24*60)*60,1000)
y <- strftime(y,format="%m/%d/%Y %H:%M")
data <- data.frame(ID=x,Starttime=y)

# you start here...
library(lubridate)     # for wday(...)
library(ggplot2)
library(RColorBrewer)  # for brewer.pal(...)

data$date <- as.POSIXct(data$Starttime, format="%m/%d/%Y %H:%M")
data$dow  <- wday(data$date)
data$cdow <- wday(data$date,label=T)
data$tod  <- as.numeric(data$date - as.POSIXct(strftime(data$date,format="%Y-%m-%d")))/60
data$bins <- cut(data$tod,breaks=1:24,labels=F)
counts    <- aggregate(ID~bins+dow,data,length)
colnames(counts)[ncol(counts)] <- "Events"

ggplot(counts, aes(x=bins,y=8-dow))+
  geom_tile(aes(fill=Events))+
  scale_fill_gradientn(colours=brewer.pal(9,"YlOrRd"),
                       breaks=seq(0,max(counts$Events),by=2))+
  scale_y_continuous(breaks=7:1,labels=c("Sun","Mon","Tues","Wed","Thurs","Fri","Sat"))+
  labs(x="Time of Day (hours)", y="Day of Week")+
  coord_fixed()
```

```{r}

# generate more illustrative dataset: you have this already
set.seed(1)
x <- 1:1000
y <- as.POSIXct("06/01/2013",format="%m/%d/%Y")+sample(0:(210*24*60)*60,1000)
y <- strftime(y,format="%m/%d/%Y %H:%M")
data <- data.frame(ID=x,Starttime=y)

# Time of day task completed
times <- as.POSIXct(data$presentationStartTime/1000, origin="1970-01-01")


times <- as.POSIXct(sessionData$start/1000, origin="1970-01-01")
sessionData$times <- times

times <- as.POSIXct(data$start/1000, origin="1970-01-01")
data$times <- times
data$end <- (data$start+data$duration) 
```
```{r}
# you start here...
library(lubridate)     # for wday(...)
library(ggplot2)
library(RColorBrewer)  # for brewer.pal(...)

data$date <- as.POSIXct(data$Starttime, format="%m/%d/%Y %H:%M")
data$dow  <- wday(data$date)
data$cdow <- wday(data$date,label=T)
data$tod  <- as.numeric(data$date - as.POSIXct(strftime(data$date,format="%Y-%m-%d")))/60
data$bins <- cut(data$tod,breaks=1:24,labels=F)
counts    <- aggregate(ID~bins+dow,data,length)
colnames(counts)[ncol(counts)] <- "Events"

ggplot(counts, aes(x=bins,y=8-dow))+
  geom_tile(aes(fill=Events))+
  scale_fill_gradientn(colours=brewer.pal(9,"YlOrRd"),
                       breaks=seq(0,max(counts$Events),by=2))+
  scale_y_continuous(breaks=7:1,labels=c("Sun","Mon","Tues","Wed","Thurs","Fri","Sat"))+
  labs(x="Time of Day (hours)", y="Day of Week")+
  coord_fixed()
```
```{r}
philly_calendar <- ggplot(clinical, aes(x = day, y = week)) + 
  geom_tile(aes(fill = userId), colour = "white") +
  facet_wrap(~text_month, scales = "free") + 
  scale_y_reverse() + 
  theme_minimal() + 
  scale_fill_viridis_c(labels = dollar) + 
  scale_x_discrete(position = "top") + 
  ylab("") + xlab("") + labs(fill = "Fines Issued") + 
  ggtitle("Philadelphia Parking Violations (2017)") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(
          size = 12, color = "black", face = "bold"), 
        plot.title = element_text(size = 14, hjust = 0.5))

philly_calendar
```


```{r}
#tasks <- read.csv("tasks.csv", header = T)

times <- as.POSIXct(clinical$start/1000, origin="1970-01-01")


clinical$times <- times
clinical$end <- (clinical$start+clinical$duration) 


# day of week
clinical$day <- weekdays(strptime(clinical$times, "%Y-%m-%d"))
week      <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
clinical$day <- factor(clinical$day, levels = week)
clinical$tod <- strftime(times, format="%H:%M:%S")
clinical$end <- (clinical$tod + 00:08:00"")
clinical$duration1 <- strftime(clinical$duration)

  strftime(clinical$duration, format="%H:%M:%S")

hour(clinical$duration)*60 + minute(clinical$duration)

Res <- as.POSIXlt(paste(Sys.Date(), clinical$duration))
Res$hour*60 + Res$min

#clinical$end <- as.POSIXct(clinical$tod, format="%H:%M:%S")


# convert time to decimal hours
clinical$start.ct   <- as.POSIXct(paste(clinical$times, clinical$start, sep = " "))
clinical$end.ct     <- as.POSIXct(paste(clinical$times, clinical$end, sep = " "))
clinical$start.hour <- as.POSIXlt(clinical$start.ct)$hour + as.POSIXlt(clinical$start.ct)$min/60 + as.POSIXlt(clinical$start.ct)$sec/3600
clinical$end.hour   <- as.POSIXlt(clinical$end.ct)$hour + as.POSIXlt(clinical$end.ct)$min/60 + as.POSIXlt(clinical$end.ct)$sec/3600

# offset clinical if > 1 per day
clinical$ymin <- c(rep(0, nrow(clinical)))
t <- table(clinical$day)
for(day in rownames(t)) {
  if(t[[day]] > 1) {
    ss <- clinical[clinical$day == day,]
    y  <- 0
    for(i in as.numeric(rownames(ss))) {
      clinical[i,]$ymin <- y
      y <- y + 1.2
    }
  }
}

```

```{r}
#week1 <- clinical 

#tasks <- read.csv("tasks.csv", header = T)



clinical$todduration<- c("00:08:00")

times <- as.POSIXct(clinical$start/1000, origin="1970-01-01")
clinical$times <- times
clinical$end <- (clinical$todduration) 


# day of week
clinical$day <- weekdays(strptime(clinical$times, "%Y-%m-%d"))
week      <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
clinical$day <- factor(clinical$day, levels = week)
clinical$tod <- strftime(times, format="%H:%M:%S")
clinical$tod <- as.POSIXct(clinical$tod, format="%H:%M:%S")
clinical$tod <- strftime(times, format="%H:%M:%S")
#clinical$tod<- as.numeric(as.character(clinical$tod))

# convert time to decimal hours
clinical$start.ct   <- as.POSIXct(paste(clinical$times, clinical$start, sep = " "))
clinical$end.ct     <- as.POSIXct(paste(clinical$times, clinical$end, sep = " "))
clinical$start.hour <- as.POSIXlt(clinical$start.ct)$hour + as.POSIXlt(clinical$start.ct)$min/60 + as.POSIXlt(clinical$start.ct)$sec/3600
clinical$end.hour   <- as.POSIXlt(clinical$end.ct)$hour + as.POSIXlt(clinical$end.ct)$min/60 + as.POSIXlt(clinical$end.ct)$sec/3600

# offset clinical if > 1 per day
clinical$ymin <- c(rep(0, nrow(clinical)))
t <- table(clinical$day)
for(day in rownames(t)) {
  if(t[[day]] > 1) {
    ss <- clinical[clinical$day == day,]
    y  <- 0
    for(i in as.numeric(rownames(ss))) {
      clinical[i,]$ymin <- y
      y <- y + 1.2
    }
  }
}



calplot <- ggplot(clinical, aes(xmin = start.hour, xmax = end.hour, 
                     ymin = ymin, ymax = ymin + 1, fill = factor(userId))) + 
  geom_rect() +
  facet_grid(day~.) + 
  theme(axis.text.y = element_blank(),
        axis.ticks = element_blank()) +
  xlim(0,23) +
  xlab("time of day")
calplot
```

```{r}
clinical$todduration <- clinical$duration %>% as.character() %>% str_split(pattern='[/.]')

```

